---
title: "DATA607 Week 2"
author: "Sergio Ortega Cruz"
date: "September 2, 2018"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Week 2

Choose six recent popular movies.  Ask at least five people that you know (friends, family, classmates, imaginary friends) to rate each of these movie that they have seen on a scale of 1 to 5.  Take the results (observations) and store them in a SQL database.  Load the information into an R dataframe.

```{r cars}
library(DBI)
library(dplyr)

#Asking Interactively for DB Password
#psswd <- .rs.askForPassword("Database Password:")
#Connecting to the Database
#con <- DBI::dbConnect(RMySQL::MySQL(), dbname = "cunydata607week2", user="root", password=passwd)
#for Markup purposes harcoded line hidden
```
```{r hidden, echo=FALSE}
con <- DBI::dbConnect(RMySQL::MySQL(), dbname = "cunydata607week2", user="root", password="espaces23")
```

```{r cont}
#Display available Data
db_list_tables(con)

```

```{r queries}
#executing several queries and getting results in Dataframes
library(ggplot2)
sql<- "SELECT * FROM movies"
res <- dbGetQuery(con,sql)
movie.catalogue <- data.frame(res)

sql2<-"SELECT  survey.rating, movies.title, movies.movie_id, users.user_name FROM survey 
 INNER JOIN movies ON survey.movie_id = movies.movie_id 
 INNER JOIN users  ON survey.user_id = users.user_id
 order by movies.title, rating desc"

moviesandratings<-data.frame(dbGetQuery(con,sql2))


qplot(title, rating, data=moviesandratings,xlab = "Rating", ylab = "Movie", main = "Individual Movie Rating by Reviewer") + facet_wrap(~user_name) + theme(axis.text.x = element_text(angle = 90, hjust = 1))
 
 
```
Showing movies per accumulated ranking

```{r accumulated}

ggplot(moviesandratings, aes(x = reorder(title, rating), y = rating, fill = title),
       xlab = 'Rating',  col = I("grey")) + geom_bar(stat = "identity") + 
  ggtitle("Movie Cummulative Ratings") +  labs(x = "Movie") +  coord_flip()

```

Now Generating a CSS parser and comparing the survey results versus IMDB (www.imdb.com) results


```{r imdbparsing}



library(rvest)


#Using CSS Selector for extracting the rating of the movie.
crazyrich <- read_html("https://www.imdb.com/title/tt3104988/?ref_=fn_al_tt_1")
CR<- crazyrich %>%html_node("strong span") %>% html_text() %>%as.numeric()

searching <- read_html("https://www.imdb.com/title/tt7668870/?ref_=fn_al_tt_1")
SE<-searching %>%html_node("strong span") %>% html_text() %>%as.numeric()

alpha <- read_html("https://www.imdb.com/title/tt4244998/?ref_=fn_al_tt_1")
AL<-alpha %>%html_node("strong span") %>% html_text() %>%as.numeric()

AXL <- read_html("https://www.imdb.com/title/tt5709188/?ref_=fn_al_tt_2")
AX<-AXL %>%html_node("strong span") %>% html_text() %>%as.numeric()

mile22 <- read_html("https://www.imdb.com/title/tt4560436/?ref_=nv_sr_1")
MI<-mile22 %>%html_node("strong span") %>% html_text() %>%as.numeric()

thenun <- read_html("https://www.imdb.com/title/tt5814060/?ref_=fn_al_tt_1")
TN<-mile22 %>%html_node("strong span") %>% html_text() %>%as.numeric()

imdbratings <- c(CR,SE,AL,AX,MI,TN)
```

```{r ratingsnorm}
imdbratings_percentage <- (imdbratings*100)/9.9

#QUERY CRAZYRICH
sqlcomp <- "select avg(rating) from survey INNER JOIN movies on survey.movie_id=movies.movie_id where movies.movie_id=1"
rescomp1 <- ((dbGetQuery(con,sqlcomp))*100)/5.5
#df.compare<- (rescomp*100)/5.5 #normalizing scale for comparison

#QUERY SEARCHING
sqlcomp <- "select avg(rating) from survey INNER JOIN movies on survey.movie_id=movies.movie_id where movies.movie_id=2"
rescomp2 <- ((dbGetQuery(con,sqlcomp))*100)/5.5

#QUERY ALPHA
sqlcomp <- "select avg(rating) from survey INNER JOIN movies on survey.movie_id=movies.movie_id where movies.movie_id=3"
rescomp3 <- ((dbGetQuery(con,sqlcomp))*100)/5.5

#QUERY AXL
sqlcomp <- "select avg(rating) from survey INNER JOIN movies on survey.movie_id=movies.movie_id where movies.movie_id=4"
rescomp4 <- ((dbGetQuery(con,sqlcomp))*100)/5.5

#QUERY MILE22
sqlcomp <- "select avg(rating) from survey INNER JOIN movies on survey.movie_id=movies.movie_id where movies.movie_id=5"
rescomp5 <- ((dbGetQuery(con,sqlcomp))*100)/5.5

#QUERY THE NUN
sqlcomp <- "select avg(rating) from survey INNER JOIN movies on survey.movie_id=movies.movie_id where movies.movie_id=6"
rescomp6 <- ((dbGetQuery(con,sqlcomp))*100)/5.5
df.compare<-c(rescomp1, rescomp2, rescomp3, rescomp4, rescomp5, rescomp6)
df.com<-as.data.frame.integer(df.compare)

df.final<-as.data.frame(imdbratings_percentage,df.com)
df.final <-(cbind(df.final,df.com))
df.final<-cbind(df.final,movie.catalogue$title)
df.final <- cbind(df.final, movie.catalogue$movie_id)
```
Showing the difference of Ratings between critics compilation on IMDB.com Vs the Survey

Showing in Blue line Survey Ratings Vs Orange dots IMDB Ratings

```{r plot2}

ggplot(df.final, aes(x= movie.catalogue$movie_id, y= imdbratings_percentage, colour="IMDB RATINGS", label=movie.catalogue$title))+ 
  geom_point() + geom_text(aes(label=movie.catalogue$title)) + geom_line (aes(y=as.numeric(df.compare)), colour="blue")

 #Closing connection to DB
DBI::dbDisconnect(con)
```




